### 2016-03-11 paper/layered_depthmap.tex
yasu

\subsection{Swarm Fusion layered depthmap estimation}
Our last problem is layered depthmap estimation, recently proposed
in~\cite{layered_depthmap} (see the anonymious paper in the
supplementary material).  The problem seeks to infer layered depthmap
representation from an RGBD image, where each layer is a piecewise
smooth segmented depthmap. This is essentially a multi-layer extension
of Surface Stereo algorithm~\cite{surface_stereo}.
%
Layered depthmap estimation is one of the most difficult kinds for MAP
inference due to its massive solution space, where the number of labels
per pixel is exponential in the number of layers. In practice, each
pixel might take an order of 100,000 \yasu{is this number correc?}
possible labels. We copy their problem formulation and the proposal
generation schemes.~\footnote{Authors have proposed a novel fusion scheme,
where a solution subspace instead of a single solution is generated by a
proposal generation scheme. Since a solution subspace is equivalent to
multiple solution proposals, their algorithm can be easily integrated
into our swarm fusion framework.  However, competing fusion methods
(e.g., Parallel Fusion Move or Hierarchical Fusion) cannot handle a
solution subspace proposal, making it impossible to conduct fair
comparative evaluations. We choose to use a simple solution proposal for
experiments in this paper.}
%Lastly, we will evaluate Swarm fusion on a very challenging layered
%depthmap estimation problem~\cite{layered_depthmap}, which has been
%recently proposed (see the anonymized pdf in the supplementary
%material).

@@

Solution proposals depend heavily on the current solution, eliminating
the possibility of using hierarchical approach, which needs to enumerate
all the proposals to start. Therefore, the only viable competing method
is Parallel Fusion Move, that replaces constant label solutions by
solution proposals in parallel alpha-expansion framework. We will also
evaluate the standard Fusion Move method.
%
The fusions are binary, for which we use QPBO.

@@

\mysubsubsection{Swarm fusion architecture}
The three swarm architectures in Fig.~\ref{fig:model} are evaluated. The
fusions are multi-way, for which we use TRW-S.

>>>>

\subsection{Swarm Fusion layered depthmap estimation}
Our last problem is layered depthmap estimation, recently proposed
in~\cite{layered_depthmap} (see the anonymous paper in the
supplementary material).  The problem seeks to infer layered depthmap
representation from an RGBD image, where each layer is a piecewise
smooth segmented depthmap. This is essentially a multi-layer extension
of Surface Stereo algorithm~\cite{surface_stereo}.
%
Layered depthmap estimation is one of the most difficult kinds in MRF
inference due to its massive solution space. The number of labels per
pixel is exponential in the number of layers, and is an order of 100,000
\yasu{is this number correc?}. We copy their problem
formulation and the proposal generation schemes.~\footnote{Authors have
proposed a novel fusion scheme, where a solution subspace instead of a
single solution is generated by a proposal generation scheme. Since a
solution subspace is equivalent to multiple solution proposals, their
algorithm can be easily integrated into our swarm fusion framework.
However, competing fusion methods (e.g., Parallel Fusion Move or
Hierarchical Fusion) cannot handle a solution subspace proposal, making
it impossible to conduct fair comparative evaluations. We choose to use
a simple solution proposal for experiments in this paper.}
%Lastly, we will evaluate Swarm fusion on a very challenging layered
%depthmap estimation problem~\cite{layered_depthmap}, which has been
%recently proposed (see the anonymized pdf in the supplementary
%material).

@@

\noindent Solution proposals depend heavily on the current solution,
eliminating the possibility of using Hierarchical Fusion, which needs to
enumerate all the proposals to start. Therefore, viable competing
methods are Fusion Move and Parallel Fusion Move.
%
%We will also evaluate the standard Fusion Move method.
%
The fusions are binary, for which we use QPBO.

@@

\mysubsubsection{Swarm fusion architectures}

\noindent The three swarm architectures with the same configurations as
in the optical flow problems have been evaluated.
%in Fig.~\ref{fig:model} are evaluated.
%The architecture parameters are exactly the same as in the optical flow problem:
%$\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
%($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
%($\alpha=1, \beta=1$) for the standard SF.
%
%The fusions are multi-way, for which we use TRW-S.

### 2016-03-11 paper/optical_flow.tex
yasu

Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
solve the optical flow problem.
%Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and proposal generation schemes for our
second problem.  We use test images in the Middlebury optical flow
benchmark~\cite{middlebury_optical_flow}.

\mysubsubsection{Competing methods} Fusion Move method in Lempitsky's
paper is the first natural contender. While they did not consider
parallel implementation, it is straightforward to combine the idea of
Parallel Alpha-Expansion and Fusion Move. Therefore, the second competing
method is ``Parallel Fusion Move (PFM)'', which is equivalent to
Parallel Alpha-Expansion with the constant label solutions replaced by
the solution proposals.
%each thread repeats generating
%a solution proposal and fusing it to the current solution. Solutions
%from all the results are sequentially fused to obtain the final solution
%as in the Parallel Alpha-Expansion method.
%
One problem of PFM is that infinite number of solution proposals can be
generated in their algorithm, and we do not know when we should stop and
perform the final sequential fusion. In our experiments, we manually
picked a time limit to initiate the final fusion.
%In Fig.~\ref{fig:model}, this computational framework corresponds to
%``parallel alpha-expansion'' with the label solutions replaced by
%solution proposals.
%
The last contender is the mix of the Hierarchical Fusion and the Fusion
Move method, dubbed ``Hierarchical Fusion Method'', where they start
from solution proposals as opposed to constant labels. One problem is
that we do not know how many solution proposals to generate to start
with. We have manually picked a good number (X \yasu{how many Hang?})
for the experiments.
%
The fusions are binary in these methods and we have used QPBO.

\mysubsubsection{Swarm fusion architectures}
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SFWSS, SFWMF, SF)
have been evaluated against the competing methods. Note that we have
used the same set of proposal generation schemes. The fusions are
multi-way, for which we have used TRW-S.
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
We have chosen $\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
($\alpha=1, \beta=1$) for the standard SF.  The fusions are multi-way,
for which we use TRW-S.

>>>>

Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
solve the optical flow problem.
%Optical flow was the problem, in which the Fusion Move method was first
%introduced by Lempitsky et al.~\cite{viktor}.
We copy their problem setting and proposal generation schemes for
our second problem.  We use images from the Middlebury optical flow
benchmark~\cite{middlebury_optical_flow}.

\mysubsubsection{Competing methods}

\noindent Fusion Move method in Lempitsky's paper is the first natural
contender. While they did not consider parallel implementation, it is
straightforward to combine the idea of Parallel Alpha Expansion and
Fusion Move. Therefore, the second competing method is ``Parallel Fusion
Move''(PFM), which is equivalent to Parallel Alpha Expansion with constant
label solutions replaced by solution proposals.
%each thread repeats generating
%a solution proposal and fusing it to the current solution. Solutions
%from all the results are sequentially fused to obtain the final solution
%as in the Parallel Alpha-Expansion method.
%
One problem of PFM is that infinite number of solution proposals can be
generated in their algorithm, and we do not know when to stop and
perform the final sequential fusion (See Parallel Alpha Expansion
architecture in Fig.~\ref{fig:model}). In our experiments, we manually
picked time limits to initiate the final fusion to make the comparisons
fair.
%In Fig.~\ref{fig:model}, this computational framework corresponds to
%``parallel alpha-expansion'' with the label solutions replaced by
%solution proposals.
%
The last contender is the mix of the Hierarchical Fusion and the Fusion
Move methods, dubbed ``Hierarchical Fusion Method''(HFM), where they
start from solution proposals as opposed to constant labels. One problem
of HFM is that the number of necessary solution proposals is unknown
before solving the problem, and the tree of labels cannot be defined. In
our experiments, we have manually picked a good number (X \yasu{how many
Hang?}) to generate proposals.
%
The fusions are binary in these methods and we have used QPBO.

\mysubsubsection{Swarm fusion architectures}

\noindent
%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
%are used to evaluate the effectiveness of our method.
The three swarm architectures in Fig.~\ref{fig:model} (SF-SS, SF-MF, SF)
have been evaluated against the competing methods. The same
configurations as in the stereo problem have been used for optical flow,
that is, $\alpha=2$ ($\beta=0$) for SF-SS, the iteration of
($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) for SF-MF, and
($\alpha=1, \beta=1$) for SF.
%
Note that we have used the same set of proposal generation schemes as
the competing methods. We have used TRW-S for multi-way fusion and QPBO
for binary fusion.
%, while our fusions are multi-way, for which we have used TRW-S.
%
% The full swarm fusion model (at the bottom right in
% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
% method. We will also try the other two Swarm fusion variants in
% Fig.~\ref{fig:model} with restrictions.
